Opt-K

### 2013-03-12 paper/paper.tex
changes
test
stuff
remove comment
changed notation in likelihood slightly
added ball tree

$$ 
P[x_t] dx^N = \prod_{i=0}^{N-1} T(x_i \rightarrow x_{i+1}) \cdot \prod_{i=0}^{N} p(x_{i} | \sigma(x_{i}))
$$
%% CRS: I think this is a better way of writing the likelihood
%% This is essentially what Liz Kellogg wrote in her likelihood.

@@

This algorithm is highly amenable to parallel computation.

>>>>

$$ 
P[x_{0...T-1}] dx^N = \prod_{i=0}^{T-1} T(x_i \rightarrow x_{i+1}) \cdot \prod_{i=0}^{N} p(x_{i} | \sigma(x_{i}))
$$

@@

This algorithm is highly amenable to parallel computation. For a euclidean
distance metric, the assignment can be sped up by using a BallTree data
structure for fast neighbor search. (We can probably actually use this
data structure within msmbuilder's assign step...)

The documentation for the sklearn cython BallTree is given here \url{http://scikit-learn.org/dev/modules/generated/sklearn.neighbors.BallTree.html#sklearn.neighbors.BallTree}
